### 2019-06-17 thesis.tex
edited astophysical plasmas

\section{Astrophysical plasmas}
\label{sec:astro-plasma}
At a first glance, the study of plasmas seems completely unrelated
with

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{corona2017.png}
%    \includegraphics[0.4\textwidth]{}
    \caption{Solar corona captured during the total solar eclipse of 2017. Credit:
      \href{https://hdr-astrophotography.com/a-propos/}{Nicolas Lefaudeux}.}
    \label{fig1}
  \end{center}
\end{figure}

@@

\subsection{Low amplitude electrostatic oscillations}
We are interested in the presence of high-frequency electrostatic
waves propagating in a homogeneous, fully ionized and unmagnetized
plasma, which is initially in equilibrium. Under such conditions,
we may consider ${\bf B=0}$. Thus, the Vlasov equation takes the
following form
\begin{equation}
  \label{vlasov-elec}
  \frac{\partial f_\alpha}{\partial t}+{\bf v \cdot \nabla}f_\alpha
+\frac{q_{\alpha}}{m_\alpha}\ {\bf E}\ {\bf\cdot \nabla_v}f_\alpha=0,
\end{equation}
where the electric field is given by
\begin{equation}
{\bf \nabla \cdot E}  = 4\pi\ \sum_\alpha q_\alpha 
\int_v  f_\alpha({\bf r},{\bf v},t) d^3v.
\label{leidegauss}
\end{equation}

@@

\autoref{fig5} shows the normalized value of the asymptotic spectrum of
$L$ waves, obtained with the use of Eq. \eqref{L,asymp}, considering a
plasma in which the ion population is described by a Maxwellian velocity
distribution, and the electron population is described by a distribution
as defined in equation \eqref{fbeta}, with $n_{\kappa e}/n_e= 0.05$. That
is, the electron distribution is a core-halo distribution, with $5\%$
of the particles in the halo population. For the evaluation of the
collisional damping and electrostatic bremsstrahlung terms, appearing
in Eq. \eqref{L,asymp}, we used Eqs. \eqref{GqL} and \eqref{PqL}, taking
into account only the Maxwellian distribution, which is a reasonable
approximation  due to the smallness of the halo population. 
\autoref{fig5}(a) shows the spectra obtained considering several values
of the index $\kappa_e$, from $\kappa_e=2.5$ to $\kappa_e=40$. It is seen
that the wave amplitude increases at the region of small values of $q$,
with the increase of $\kappa_e$. It is also seen that in the case of
fairly large value of $\kappa_e$, as $\kappa_e=40$, the spectrum obtained
in the case of a core-halo distribution is very close to the spectrum
obtained in the case of a purely Maxwellian electron distribution, which
can be obtained from equation \eqref{L,asymp} by taking $n_{\kappa e}=0$.
It is also seen that in the case of small values of $\kappa_e$ the
asymptotic spectrum is qualitatively very similar to the spectrum
obtained after the time evolution of the system, taking into account
the new effects of electrostatic bremsstrahlung and collisional damping,
shown in Figure 1 of Ref. \cite{Tigik2017a}. For comparison, we
show in figure \autoref{fig5}(b) the asymptotic spectrum of $L$ waves
which would be obtained by neglecting the new effects, of collisional
bremsstrahlung and collisional damping.
% \begin{figure}[h]
%   \begin{center}
%     %% \hspace{-0.42cm}
%     \includegraphics[scale=0.5,angle=270]{IL1D_005kvar.eps}
%     \includegraphics[scale=0.5,angle=270]{IL1D_005kvarno-brem.eps}
%     \caption{Asymptotic spectrum of Langmuir waves for several values
%       of $\kappa$ index and Maxwellian distribution. (a) With electrostatic
%     bremsstrahlung emission and collisional damping.
%    (b) Without bremsstrahlung emission and collisional damping.}
%     \label{fig5}
%   \end{center}
% \end{figure}

>>>>

\section{Astrophysical plasmas}
\label{sec:astro-plasma}
On Earth, the plasma is considered an exotic state of matter, associated to the
glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
laboratories, and the promise of cleaner and technically infinite energy source
when scientists and engineers manage to succeed at obtaining a controlled, and
energetically efficient, thermonuclear fusion. Naturally occurring plasmas in our
everyday life are rare, restricted to the occurrence of lightning during storms
and beautiful auroras that are spotted at high latitudes. In the interplanetary
and interstellar space, however, the situation is the opposite. Starting in the
outer layers of Earth's atmosphere, passing through the solar wind in the
interplanetary space, to the stellar interiors and atmospheres, accretion disks,
and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of
the observable matter is in the plasma state \cite{may}.

% Astrophysics is a millennial observational science, that started with bare eyes
% observation of the sky, describing the constellations, and solar, lunar and
% planetary cycles. These first observations of the relative motion of planetary
% bodies led to solar clocks, calendars, and navigation charts. Nowadays, we have
% extremely sophisticated equipment of observation, both on Earth and in space,
% that can reach

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{corona2017.png}
    \includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
    \caption{Solar corona captured during the total solar eclipse of 2017.
      {\footnotesize Credit:}
      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
    \label{fig1}
  \end{center}
\end{figure}

@@

\section{Low amplitude electrostatic oscillations}
We are interested in the presence of high-frequency electrostatic
waves propagating in a homogeneous, fully ionized and unmagnetized
plasma, which is initially in equilibrium. Under such conditions,
we may consider ${\bf B=0}$. Thus, the Vlasov equation takes the
following form
\begin{equation}
  \label{vlasov-elec}
  \frac{\partial f_\alpha}{\partial t}+{\bf v \cdot \nabla}f_\alpha
+\frac{q_{\alpha}}{m_\alpha}\ {\bf E}\ {\bf\cdot \nabla_v}f_\alpha=0,
\end{equation}
where the electric field is given by
\begin{equation}
{\bf \nabla \cdot E}  = 4\pi\ \sum_\alpha q_\alpha 
\int_v  f_\alpha({\bf r},{\bf v},t) d^3v.
\label{leidegauss}
\end{equation}

@@

\autoref{fig5} shows the normalized value of the asymptotic spectrum of
$L$ waves, obtained with the use of Eq. \eqref{L,asymp}, considering a
plasma in which the ion population is described by a Maxwellian velocity
distribution, and the electron population is described by a distribution
as defined in equation \eqref{fbeta}, with $n_{\kappa e}/n_e= 0.05$. That
is, the electron distribution is a core-halo distribution, with $5\%$
of the particles in the halo population. For the evaluation of the
collisional damping and electrostatic bremsstrahlung terms, appearing
in Eq. \eqref{L,asymp}, we used Eqs. \eqref{GqL} and \eqref{PqL}, taking
into account only the Maxwellian distribution, which is a reasonable
approximation  due to the smallness of the halo population. 
\autoref{fig5}(a) shows the spectra obtained considering several values
of the index $\kappa_e$, from $\kappa_e=2.5$ to $\kappa_e=40$. It is seen
that the wave amplitude increases at the region of small values of $q$,
with the increase of $\kappa_e$. It is also seen that in the case of
fairly large value of $\kappa_e$, as $\kappa_e=40$, the spectrum obtained
in the case of a core-halo distribution is very close to the spectrum
obtained in the case of a purely Maxwellian electron distribution, which
can be obtained from equation \eqref{L,asymp} by taking $n_{\kappa e}=0$.
It is also seen that in the case of small values of $\kappa_e$ the
asymptotic spectrum is qualitatively very similar to the spectrum
obtained after the time evolution of the system, taking into account
the new effects of electrostatic bremsstrahlung and collisional damping,
shown in Figure 1 of Ref. \cite{Tigik2017a}. For comparison, we
show in figure \autoref{fig5}(b) the asymptotic spectrum of $L$ waves
which would be obtained by neglecting the new effects, of collisional
bremsstrahlung and collisional damping.
\begin{figure}[h]
  \begin{center}
    %% \hspace{-0.42cm}
    \includegraphics[scale=0.5,angle=270]{IL1D_005kvar.eps}
    \includegraphics[scale=0.5,angle=270]{IL1D_005kvarno-brem.eps}
    \caption{Asymptotic spectrum of Langmuir waves for several values
      of $\kappa$ index and Maxwellian distribution. (a) With electrostatic
    bremsstrahlung emission and collisional damping.
   (b) Without bremsstrahlung emission and collisional damping.}
    \label{fig5}
  \end{center}
\end{figure}
